IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-10-18 paper/concrete.tex
Pass Section 4

The operational semantics we have defined in the previous section
satisfy non-interference by design.
We achieve this general statement that works for a large class of
languages by having different tasks executing completely isolated from
each other, such that every task has its own state.
In some cases, this strong separation is desirable, or even necessary.
Languages like C provide direct access to memory locations without
mechanisms in the language to achieve a separation of the heap.
On the other hand, for other languages this
strong isolation of tasks can be
undesirable, e.g., for performance reasons.
For instance, for the language |targetLangML|, our presentation so far
requires a separate heap per task, which is not very practical.
Instead, we would like to
more tightly couple the integration of the target and IFC
language by reusing existing infrastructure.  In the running example,
a concrete implementation might use a single global heap.
More precisely, instead of using a configuration of the form
$|iconf iS (fullconf id1 il1 tS1 ie1, fullconf id2 il2 tS2 ie2 ldots)|$
we would like a single global heap as in
$|oneheapiconf iS tS (oneheapfullconf id1 il1 ie1, oneheapfullconf id2 il2 ie2, ldots)|$

If the operational rules are adapted na\"ively to this new setting,
then non-interference can be violated: as we mentioned earlier,
shared mutable cells could result in violation of noninterference.
What we would like is a way of characterizing safe modifications to
the semantics which preserve non-interference.
The intention of our single heap implementation is to permit
efficient execution while \emph{conceptually maintaining isolation between
tasks} (by not allowing sharing of references between them).
This intuition of having a different (potentially more efficient)
concrete semantics that behave like the abstract semantics
can be formalized by the following definition:

@@

A better solution is to forbid sandboxed expressions as well
as messages sent to other tasks to contain memory addresses in the
first place.  In a statically typed language, the type system could
prevent this from happening, and we talk more about how our
approach integrates with typed languages in
Section~\ref{sec:extensions:types}.
In dynamically typed languages such as |targetLangML|, we might
restrict the transition for |sandbox| and |send| to only allow expressions
without memory addresses.

>>>>

The operational semantics we have defined in the previous section
satisfy non-interference by design.
We achieve this general statement that works for a large class of
languages by having different tasks executing completely isolated from
each other, such that every task has its own state.
In some cases, this strong separation is desirable, or even necessary.
Languages like C provide direct access to memory locations without
mechanisms in the language to achieve a separation of the heap.
On the other hand, for other languages, this
strong isolation of tasks can be
undesirable, e.g., for performance reasons.
For instance, for the language |targetLangML|, our presentation so far
requires a separate heap per task, which is not very practical.
Instead, we would like to
more tightly couple the integration of the target and IFC
language by reusing existing infrastructure.  In the running example,
a concrete implementation might use a single global heap.
More precisely, instead of using a configuration of the form
$|iconf iS (fullconf id1 il1 tS1 ie1, fullconf id2 il2 tS2 ie2 ldots)|$
we would like a single global heap as in
$|oneheapiconf iS tS (oneheapfullconf id1 il1 ie1, oneheapfullconf id2 il2 ie2, ldots)|$

If the operational rules are adapted na\"ively to this new setting,
then non-interference can be violated: as we mentioned earlier,
shared mutable cells could result in violation of non-interference.
What we would like is a way of characterizing safe modifications to
the semantics which preserve non-interference.
The intention of our single heap implementation is to permit
efficient execution while \emph{conceptually maintaining isolation between
tasks} (by not allowing sharing of references between them).
This intuition of having a different (potentially more efficient)
concrete semantics that behave like the abstract semantics
can be formalized by the following definition:

@@

A better solution is to forbid sandboxed expressions as well
as messages sent to other tasks to contain memory addresses in the
first place.  In a statically typed language, the type system could
prevent this from happening.
%, and we talk more about how our
%approach integrates with typed languages in
%Section~\ref{sec:extensions:types}.
In dynamically typed languages such as |targetLangML|, we might
restrict the transition for |sandbox| and |send| to only allow expressions
without memory addresses.
